Import_OlisData

### 2024-03-18 Code/Import_OlisData.Rmd
New file path to Culture Catalog
minor edit

Import_OlisData.Rmd imports OLIS CLARiTY spectrophotometer files from Data/RawData/OlisData.zip folder and stored in Data/ImportedData/ImportedOlisData folder as: 
Baltic_Photoperiod_Imported_OlisData.Rds

@@

# Read MetaData
```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data","CultureCatalog.Rds"))

>>>>

Import_OlisData.Rmd imports OLIS 14 UV/VIS Clarity spectrophotometer files from Data/RawData/OlisData.zip folder and stored in Data/ImportedData/ImportedOlisData folder as: 
PICO_Imported_OlisData.Rds

@@

# Read MetaData
```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data","RawData" ,"CultureCatalog.Rds"))
